# Visualization {#Visualization}

*ggplot2* is a powerful package for data visualization in R. Most of the figures in this chapter are plotted using *ggplot2*. Other great packages such as *VennDiagram*, *UpSetR*, and *ComplexHeatmap* are used to generate special figures like Venn diagram, UpSet, and Heatmap, etc. 


```{r eval=TRUE}
library(ggplot2)
```



## Volcano plot

```{r eval=TRUE}
library(ggrepel)

dataForVolcanoPlot <- readRDS(file='data/dataForVolcanoPlot.rds')
head(dataForVolcanoPlot)

logFcThreshold <- log(2)
adjPvalThreshold <- 0.05


dataForVolcanoPlot$Significance[with(dataForVolcanoPlot, logFC < logFcThreshold | FDR > adjPvalThreshold)] <- 'NS'
dataForVolcanoPlot$Significance[with(dataForVolcanoPlot, logFC >= logFcThreshold & FDR <= adjPvalThreshold)] <- 'UP'
dataForVolcanoPlot$Significance[with(dataForVolcanoPlot, logFC <= -logFcThreshold & FDR <= adjPvalThreshold)] <- 'DOWN'


ggplot(dataForVolcanoPlot, aes(x = logFC, y = -log10(FDR))) +
  #xlim(-7.5,7.5) 
  xlab(expression('log'[2]*'(Fold Change)')) + ylab(expression('-log'[10]*'(FDR)')) +
  geom_point(aes(color=Significance), alpha=1, size=2) +
  geom_vline(xintercept = c(-logFcThreshold, logFcThreshold), 
             color='darkgreen', linetype='dashed') +
  geom_hline(yintercept = -log10(adjPvalThreshold), color='darkgreen',linetype='dashed')+
  scale_x_continuous(breaks=c(-4,-2,0,2,4,6,8,10)) +
  scale_color_manual(values = c('green3',"black", "red")) + 
  geom_text_repel(data = subset(dataForVolcanoPlot, FDR < 10^-40 & logFC > log(2)), segment.alpha = 0.4,
                  aes(label = symbol), size = 3.5, color='red', segment.color = 'black') +
  geom_text_repel(data = subset(dataForVolcanoPlot, FDR < 10^-40 & logFC < log(2)*-1), segment.alpha = 0.4,
                  aes(label = symbol), size = 3.5, color='green3', segment.color = 'black') +
  theme_gray() +
  theme(legend.position="none") +
  theme(axis.text=element_text(size=14), 
        axis.title=element_text(size=16),
        strip.text = element_text(size=14)) +
  theme(plot.margin =  margin(t = 0.25, r = 0.25, b = 0.25, l = 0.25, unit = "cm"))

```








## Barplot


## Boxplot


## Scatter plot


## Venn Diagram


## UpSet plot

```{r eval=TRUE}

library(UpSetR)

A <- sample(1:1000, 400, replace = FALSE);
B <- sample(1:1000, 600, replace = FALSE);
C <- sample(1:1000, 350, replace = FALSE);
D <- sample(1:1000, 550, replace = FALSE);
E <- sample(1:1000, 375, replace = FALSE);
G <- sample(1:1000, 200, replace = FALSE);
H <- sample(1:1000, 777, replace = FALSE);

dataForUpSetPlot <- list(A=A, B=B, C=C, D=D, E=E, G=G, H=H)
setsBarColors <- c('#EA4335', '#FBBC05', '#34A853', '#4285F4')

### sort by degree
upset(fromList(dataForUpSetPlot),
      nsets=length(dataForUpSetPlot),
      nintersects = 1000,
      sets = c("A", "B", "C", 'D'),
      #keep.order = TRUE,
      point.size = 3,
      line.size = 1,
      number.angles = 0,
      text.scale = c(1.5, 1.2, 1.2, 1, 1.5, 1), # ytitle, ylabel, xtitle, xlabel, sets, number
      order.by="degree",
      matrix.color="black",
      main.bar.color = 'black',
      mainbar.y.label = 'Intersection Size',
      sets.bar.color=setsBarColors,
      queries = list(list(query = intersects,
           params = list('A','B','C'), color = "orange", active = T)))


```





## Heatmap


## Bubble plot


## Radar plot



